\chapter{Language Overview}


\section{The computational model}
Sound processing DSL would likely involve performing 
mathematical operations on audio data. This could include 
operations such as filtering, equalization, time stretching, pitch 
shifting, and more. These operations would typically be performed 
on a digital representation of the audio waveform, such as a 
sequence of samples.

The computational model for performing these operations would 
likely involve designing algorithms and data structures for 
representing and manipulating audio data. These algorithms would 
need to take into account factors such as sample rate, bit depth, 
and channel count, as well as the specific operations being 
performed.

\section{Basic data structures}
For creating a fully fledged DSL for sound processing we would like 
to implement the following data structures: 

An audio buffer which is a fixed-length array of samples that 
represents an audio signal. It is the fundamental data structure 
used to represent audio data in a digital audio system. The audio 
buffer can be used to store audio signals before and after 
processing.

Filters are commonly used in audio processing to manipulate audio 
signals. Digital filters, such as Finite Impulse Response (FIR) or 
Infinite Impulse Response (IIR), are often represented using 
coefficients that are stored in arrays or matrices.

A spectrogram is a visual representation of the spectrum of 
frequencies of an audio signal as it changes over time. Spectrograms 
can be represented as a matrix or a multi-dimensional array, where 
each element represents the energy of a frequency at a specific 
time.

If your DSL supports music composition, musical notation can be 
used to represent the pitch, duration, and timing of notes. Musical 
notation can be represented using data structures such as lists or 
trees, where each element represents a note or a chord.

\section{Basic control structures}
Our DSL will have the following control structures to provide the 
user with a tool for sound manipulation:

Functions are commonly used to manipulate audio signals in a DSL 
for sound processing. For example, you might define functions to 
apply filters, equalization, or other transformations to an audio 
signal.

Loops can be used to process audio signals in real-time or to 
iterate over a sequence of audio samples. For example, you might 
use a loop to apply an effect to a section of an audio signal.
Conditionals can be used to apply different processing to an audio 
signal depending on the values of certain parameters or 
variables.Events can be used to trigger changes in the sound, such 
as starting or stopping a sound effect or changing the volume.

The user interface for the DSL can be designed to provide a 
variety of ways for users to manipulate sound. This can include 
graphical user interfaces, command-line interfaces, or even 
physical controllers such as MIDI keyboards or DJ mixers.
The user can manipulate sound in your DSL using these control 
structures and interfaces. For example, a user might write a 
function to filter out high-frequency noise in an audio signal or 
use a loop to create a repeating pattern of notes. The user might 
also adjust parameters such as volume, tempo, or filter cutoff 
frequency using the user interface.

\section{Inputs and outputs of the DSL}
\par The most common input methods would include:
\begin{itemize}
    \hitem Audio files: Audio files can be used as input to your 
    DSL, allowing users to load existing audio recordings or sound 
    effects to be processed,
    \hitem Real-time audio: Real-time audio can be used as input to 
    your DSL, allowing users to process audio signals in real-time 
    as they are generated by microphones or other sources,
    \hitem MIDI data: MIDI data can be used as input to your DSL, 
    allowing users to control synthesizers or other instruments in 
    real-time.
\end{itemize}

The output formats would be the same as the input ones but they 
would obviously be modified by the script given by the user.

\section{Error handling}
Error handling is an important aspect of any programming language, 
including a DSL (Domain Specific Language) for sound processing. 
Our DSL should provide a clear and consistent mechanism for 
detecting and reporting errors to users.

Exceptions can be used to handle errors that occur during runtime. 
When an exception is thrown, your DSL can display an error message 
to the user and terminate the program or, in some cases, try to 
recover from the error and continue execution.
Our DSL will include validation checks to catch errors before they 
occur during runtime. For 
example, you might check that a user-provided file exists and is in 
the correct format before attempting to load it. Validation can 
help prevent errors that might otherwise result in exceptions or 
unexpected behavior.

Warnings can be used to alert users to potential issues that do not 
necessarily prevent execution of the program. For example, your DSL 
might display a warning when a user sets a parameter value outside 
of a recommended range, but still allow the program to execute.
Our DSL can provide debugging tools to help users diagnose errors 
during runtime. For example, you might provide a way for users to 
inspect the values of variables or print debugging messages to the 
console.

Clear documentation can help users understand how to use your DSL 
and avoid errors. Your DSL should provide documentation that 
describes its features and functionality, as well as any 
limitations or constraints that users should be aware of.
